---
output:
  github_document:
    html_preview: false
---

```{r,echo=FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="man/figures/"
)
```

# biblio

An R-package to manage bibliographic references. This package is focused on
data import-export to a data frame format based on the software
[**JabRef**](http://www.jabref.org/).

## Installing biblio

You can install this package from **GitHub**.

```{r, eval=FALSE}
library(remotes)
install_github("kamapu/biblio")
```

A copy of the references cited in the book of [Luebert & Pliscoff
(2016)](https://doi.org/10.5281/zenodo.60800) is also installed with this
package.

```{r}
library(biblio)
Bib <- read_bib(bib=file.path(path.package("biblio"), "LuebertPliscoff.bib"))
Bib
```

A "fake" r-markdown document is also installed to test the
function `match_keys()`, which is able to recognize the bibtexkeys in use
within an r-markdown docuemnt.

```{r}
cited_refs <- match_keys(x=Bib, rmd_file=file.path(path.package("biblio"),
				"document.Rmd"))
cited_refs
```

The output shows the respective bibtexkey by its occurrence in the document
(line number).
With this output it is also possible to do some statistics.

```{r}
stats_refs <- aggregate(line ~ bibtexkey, data=cited_refs, FUN=length)

# Number of citations in text
sum(stats_refs$line)

# Number of cited articles
nrow(stats_refs)

# Respective frequency to know rare citations in text
stats_refs[order(stats_refs$line), ]
```
